The Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2013-10-19 papers/pair-correlation/paper.tex
add text to results section of pair paper Tested on collins. Took 0:22.07.
format long equation more nicely Tested on collins. Took 0:24.47.

Just as the radial distribution function of a homogeneous fluid may be
computed from the density of an inhomogeneous one using Percus'
test-particle trick, the triplet distribution function of a
homogeneous system can be computed using an approximation of the pair
distribution for an inhomogeneous fluid, such as we have developed.
\begin{align}
  g^{(3)}(\rr_1,\rr_2,\rr_3) &= \frac{n_{\textrm{TP}(\rr_1)}(\rr_2)
  n_{\textrm{TP}(\rr_1)}(\rr_3)}{n^2}
  g^{(2)}_{\textrm{TP}(\rr_1)}(\rr_2,\rr_3)
\end{align}
where $g^{(3)}(\rr_1,\rr_2,\rr_3)$ is the triplet distribution
function of a homogeneous fluid with density $n$, and the
$\textrm{TP}(\rr_1)$ subscript indicates quantities computed for the
inhomogeneous density configuration in which one sphere is fixed at
position $\rr_1$.  This method treats one of the three positions---the
location of the test particle---differently from the others, which
means that a poor approximation to the pair distribution function may
beak the symmetry which is present in the true triplet distribution
function.

>>>>

Just as the radial distribution function of a homogeneous fluid may be
computed from the density of an inhomogeneous one using Percus'
test-particle trick, the triplet distribution function of a
homogeneous system can be computed using an approximation of the pair
distribution for an inhomogeneous fluid, such as we have developed.
\begin{multline}
    g^{(3)}(\rr_1,\rr_2,\rr_3) =\\
    \frac{n_{\textrm{TP}(\rr_1)}(\rr_2)
      n_{\textrm{TP}(\rr_1)}(\rr_3)}{n^2}
    g^{(2)}_{\textrm{TP}(\rr_1)}(\rr_2,\rr_3)
\end{multline}
where $g^{(3)}(\rr_1,\rr_2,\rr_3)$ is the triplet distribution
function of a homogeneous fluid with density $n$, and the
$\textrm{TP}(\rr_1)$ subscript indicates quantities computed for the
inhomogeneous density configuration in which one sphere is fixed at
position $\rr_1$.  This method treats one of the three positions---the
location of the test particle---differently from the others, which
means that a poor approximation to the pair distribution function may
beak the symmetry which is present in the true triplet distribution
function.
